\problemname{Spies Like Us}
The Ultrasecret Spy Organization is very concerned about recent leads concerning a secret con-
spiracy involving the use of the Comic Sans font.

In order to avoid groupthink, the Ultrasecret Spy Organization has decided to divide its agents in
two groups. Each of the two groups will carry its own investigation. However, occassionally
interaction between members of different groups will happen through some previously designated
contact points (i.e.\ two people on different teams that are allowed to speak with each other in
special circumstances). This has to be made in a way that preserves the fact that there is not much
communication between the teams. To make this rule more exact, two people on the same team can have
no more than one common contact on the other team.

You are given a plan for the contact points between the two groups. Your task is to determine
whether this actually satisfies the constraint that two people on the same team can have no more
than one common contact in the other team.

\section*{Input}
The first line of the input file will contain two space-separated integers $N$ and $M$, $(1 \le N, M
\le 2000)$. They represent the number of people in each of the teams. The next line will contain an
integer $K$, $(0 \le K \le NM)$. Each of the following $K$ lines will containing two integers $i$
and $j$, with $(1 \le i \le N, 1 \le j \le M)$. This input will represent that person $i$ of the
first team and person $j$ of the second team are allowed to communicate with each other.

For test cases worth 25\% of the marks, you may assume $N, M \le 200$.

\section*{Output}
For each input, you will output one line. Its content will be YES, if the proposal satifies the
constraint that two people on the same team can have no more than one common contact on the
other team, and NO otherwise.
