\problemname{WordSpin}

\v{Z}ofka invented a new word puzzle. She gives you two strings $s_1$ and $s_2$ of the same length. You need to modify $s_1$ into $s_2$ as quickly as possible. The trick is that you are allowed to modify the strings only using the following types of moves: (1) shift forward where you choose a substring of one of the strings and shift each of its letters by 1 forward in the alphabet, or (2) shift backward where you shift each letter in a substring backward in the alphabet. The first move is not allowed if the substring contains the letter {\tt z} while the second move is not allowed if the subtring contains {\tt a}. What is the smallest number of moves you need to modify $s_1$ into $s_2$?

\section*{Input}
The first line contains $k$, the number of word puzzles.
Each word puzzle is described on a single line that contains the strings $s_1$ and $s_2$ separated
by space. The strings contain only lower case letters. You may also assume that the length of each
string is at most $10\,000\,000$.


\section*{Output}
The output contains $k$ lines. The $i$-th line corresponds to the $i$-th word puzzle.
It contains the smallest number of moves needed to modify $s_1$ into $s_2$.


\section*{Note}
The first sample input can be modified in the following way. First shift {\tt lo} forward, getting
{\tt helmp}. Then shift {\tt h} forward 12 times, getting {\tt telmp}. Then shift {\tt l} 11 times
backward to get {\tt teamp} and then shift {\tt p} forward three times to get {\tt teams}. Total
number of moves is $1+12+11+3=27$.

The second sample input can be modified as follows. First shift the entire string forward, getting {\tt bbdddbbbb}. Then shift {\tt ddd} backward twice to get {\tt bbbbbbbbb}. This requires 1+2=3 moves.
